Characterization of an anionic membrane mimetic with natural phospholipid content and magnetic orienting capabilities

### 2020-08-31 revision_cover_letter.tex
Razón para masas en gramos añadida

\item Reviewer 1 said \textit{What was the reason to use 8 mg benzocaine and 7 mg levoDOPA? If the authors took the molecular weight of the drugs into consideration, why did they choose to express concentrations in g and not as molar ratios (regarding the bicelle’s components)?}

\item Reviewer 1 said: \textit{It would be interesting to include information on the partition coefficient of both drugs.}\\
  Agreed. It has been included in the revised manuscript.

>>>>

\item Reviewer 1 said \textit{What was the reason to use 8 mg benzocaine and 7 mg levoDOPA? If the authors took the molecular weight of the drugs into consideration, why did they choose to express concentrations in g and not as molar ratios (regarding the bicelle’s components)?}\\
Bicelle components were expressed in weight percentages to ease an eventual future reproduction of the mesophase.
\item Reviewer 1 said: \textit{It would be interesting to include information on the partition coefficient of both drugs.}\\
  Agreed. They have been included in the revised manuscript.
